Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-25 article.tex
Copy for Yoav

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\bm{\mathcal{S}}}
\newcommand{\OpRot}{\bm{\mathcal{R}}}
\newcommand{\OpDistance}{\bm{\mathcal{D}}}
\newcommand{\OpCumsum}{\bm{\mathcal{C}}}
\newcommand{\OpInt}{\bm{\mathcal{I}}}
\newcommand{\OpCamera}{\bm{\mathcal{P}}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
samples the optical radiance distribution in location and
direction. It is mainly used in small-scale setups. This paper deals
with a huge scale, up to Earth's size.  The atmosphere allows light to
pass through in multiple locations and directions. Light is affected
by this medium. Therefore, in this paper we lay out a principle to
recover this 3D medium using measured and modeled lightfields
(Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \includegraphics[width=\linewidth]{images/groundtomog24.pdf}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
Projecting this large object to various directions is similar to
tomography in other scientific domains. However, the formulation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect volcanic gas~\cite{wright}, which absorbs
UV. Other gases in the atmosphere absorb IR. However, in visible
light, atmospheric attenuation is typically dominated by {\em
  scattering} by particles (aerosols), rather than absorption by
gasses. Thus, in our problem, we cannot rely on direct illumination,
but on sunlight scattered into the LOS.  The model turns out to be
{\em nonlinear, yet tractable}.

@@

{\em Lightfield}, or {\em integral}
imaging~\cite{Ng2006,bishop,Ng1948}, samples the radiance distribution
in location and direction. It has so far been used in small-scale
setups. Our proposed research deals with huge scale, up to Earth's
size. Capturing the lightfield in very large scales requires uncommon
sensors. Sampling Earth both spatially and angularly is done by the
Multiangle Imaging SpectroRadiometer (MISR)~\cite{Martonchikc} from
space (\cref{fig:misr}), the Airborne Multiangle SpectroPolarimetric
Imager (AirMSPI)~\cite{dinerDavis10}, and other spaceborne and
airborne instruments.
\begin{figure}[t]
  \centering
  \includegraphics[width=0.90\textwidth]{misr.pdf}
  \caption{\small{[Left] NASA's MISR instrument, developed by the Jet
      Propulsion Laboratory (JPL), provides multiangular,
      multispectral images of Earth.  It scans Earth from 9 view
      angles, at resolution of $\approx 300$m.  [Right] A series of
      MISR images from different viewing angles showing an assortment
      of clouds over Florida.}  }
  \label{fig:misr}
\end{figure}

@@

We believe that high resolution atmospheric recovery can be achieved
by a large set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upwards and capturing the sky lightfield.  This
paper takes the first step, of formulating this principle and
demonstrating feasibility using realistic simulations. The formulation
of this paper can also apply to multiview images that are captured
from satellites, for future spaceborne instruments of this capacity.

We simulate image acquisition using Monte Carlo simulations
(\cref{sec:monte-carlo-simul}).  Monte carlo model multiple scattering
and therefore enable simulating realistic scenarios. Our
reconstruction algorithm is based on the Single-Scattering model
(\cref{sec:single-scatt-model}). The Single-Scattering approximation
enables state the solution to the Radiative Transform in a closed
form. This closed is beneficial to us as it enables us to invert the
model and thus recover the underlying atmosphere
(\cref{sec:inverse-problem}).

@@

\noindent{\bf Cameras}: The cameras are created by the MC simulations.
Each ground-based camera has a hemispherical field of view, capturing
the entire sky from its viewpoint. Again, we used different numbers of
cameras ranging from 100 viewpoints to 12. The cameras are arranged on
a grid.  The resolution of each camera is low, expressing the fact
that cloudless (yet hazy) sky images are rather smooth, hence there is
no need for high image resolution.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.7\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MCRT simulation (\cref{sec:monte-carlo-simul}).}
  \label{fig:simulation-results1}
\end{figure}
of the {\em Haze Blobs} scene that corresponds to
\cref{fig:two_clouds_sim}a.

>>>>

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\bm{\mathcal{S}}}
\newcommand{\OpRot}{\bm{\mathcal{R}}}
\newcommand{\OpDistance}{\bm{\mathcal{D}}}
\newcommand{\OpCumsum}{\bm{\mathcal{C}}}
\newcommand{\OpInt}{\bm{\mathcal{I}}}
\newcommand{\OpCamera}{\bm{\mathcal{P}}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
%\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

Lightfield and integral imaging~\cite{bishop,horstmeyer,kim,Ng1948}
samples the optical radiance distribution in location and
direction. It is mainly used in small-scale setups. This paper deals
with a huge scale, up to Earth's size.  The atmosphere allows light to
pass through in multiple locations and directions. Light is affected
by this medium. Therefore, in this paper we lay out a principle to
recover this 3D medium using measured and modeled lightfields
(Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
Projecting this large object to various directions is similar to
tomography in other scientific domains. However, the formulation here
is distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{gorbunov,messer}. In contrast,
our source is the uncontrolled, unidirectional Sun. Moreover, typical
tomography relies on a linear model~\cite{gregson}: the pixel value is
a linear combination of components along a line of sight (LOS), or a
multiplicative combination (linearized by a logarithm). Linear
tomography can detect volcanic gas~\cite{wright}, which absorbs
UV. Other gases in the atmosphere absorb IR. However, in visible
light, atmospheric attenuation is typically dominated by {\em
  scattering} by particles (aerosols), rather than absorption by
gasses. Thus, in our problem, we cannot rely on direct illumination,
but on sunlight scattered into the LOS.  The model turns out to be
{\em nonlinear, yet tractable}.

@@

{\em Lightfield}, or {\em integral}
imaging~\cite{Ng2006,bishop,Ng1948}, samples the radiance distribution
in location and direction. It has so far been used in small-scale
setups. Our proposed research deals with huge scale, up to Earth's
size. Capturing the lightfield in very large scales requires uncommon
sensors. Sampling Earth both spatially and angularly is done by the
Multiangle Imaging SpectroRadiometer (MISR)~\cite{Martonchikc} from
space, the Airborne Multiangle SpectroPolarimetric
Imager (AirMSPI)~\cite{dinerDavis10}, and other spaceborne and
airborne instruments.

@@

We believe that high resolution atmospheric recovery can be achieved
by a large set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upward and capturing the sky lightfield.  This
paper takes the first step, of formulating this principle and
demonstrating feasibility using realistic simulations. The formulation
of this paper can also apply to multiview images that are captured
from satellites, for future spaceborne instruments of this capacity.

Our reconstruction algorithm is based on the
Single-Scattering model (\cref{sec:single-scatt-model}). The
Single-Scattering approximation enables stating an analytic solution
to the Radiative Transfer in a closed form. This closed form is
beneficial to us as it enables us to invert the model and thus recover
the underlying atmosphere (\cref{sec:inverse-problem}). We validate
our reconstruction method by applying it on 'Realistic' images.
We simulate image acquisition using Monte Carlo (MC) simulations
(\cref{sec:monte-carlo-simul}).  The monte carlo method models
multiple scattering and therefore enables simulating realistic
scenarios.

@@

\noindent{\bf Cameras}: The cameras are created by the MC simulations.
Each ground-based camera has a hemispherical field of view, capturing
the entire sky from its viewpoint. Again, we used different numbers of
cameras ranging from 100 viewpoints to 12. The cameras are arranged on
a grid.  The resolution of each camera is low, expressing the fact
that cloudless (yet hazy) sky images are rather smooth, hence there is
no need for high image resolution.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MCRT simulation (\cref{sec:monte-carlo-simul}).
    [c] Cross section along the 
  }
  \label{fig:simulation-results1}
\end{figure}
of the {\em Haze Blobs} scene that corresponds to
\cref{fig:two_clouds_sim}a.
